Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-08-03 output/latex/manuscript.tex
latex: add eMERGE Consortium as author

Milton Pividori\textsuperscript{1,2},
Sumei Lu\textsuperscript{3},
Binglan Li\textsuperscript{4},
Chun Su\textsuperscript{3},
Matthew E. Johnson\textsuperscript{3},
Wei-Qi Wei\textsuperscript{5},
Qiping Feng\textsuperscript{5},
Bahram Namjou\textsuperscript{6},
Krzysztof Kiryluk\textsuperscript{7},
Iftikhar Kullo\textsuperscript{8},
Yuan Luo\textsuperscript{9},
Blair D. Sullivan\textsuperscript{10},
Benjamin F. Voight\textsuperscript{11,12,13},
Carsten Skarke\textsuperscript{13},
Marylyn D. Ritchie\textsuperscript{1},
Struan F.A. Grant\textsuperscript{3,14,15,1},
Casey S. Greene~\textsuperscript{\protect\hyperlink{correspondence}{\Letter}} \textsuperscript{16,2}

@@

\textsuperscript{1} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{2} Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{3} Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA 19104, USA.
\textsuperscript{4} Department of Biomedical Data Science, Stanford University, Stanford, CA 94305, USA.
\textsuperscript{5} Vanderbilt University Medical Center, Nashville, TN 37232, USA.
\textsuperscript{6} Cincinnati Children's Hospital Medical Center, Cincinnati, OH 45229, USA.
\textsuperscript{7} Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, NY 10032, USA.
\textsuperscript{8} Mayo Clinic, Rochester, MN 55905, USA.
\textsuperscript{9} Northwestern University, Chicago, IL 60611, USA.
\textsuperscript{10} Kahlert School of Computing, University of Utah, Salt Lake City, UT 84112, USA.
\textsuperscript{11} Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{12} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{13} Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{14} Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{15} Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA.
\textsuperscript{16} Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA.

@@

>>>>

Milton Pividori\textsuperscript{1,2},
Sumei Lu\textsuperscript{3},
Binglan Li\textsuperscript{4},
Chun Su\textsuperscript{3},
Matthew E. Johnson\textsuperscript{3},
Wei-Qi Wei\textsuperscript{5},
Qiping Feng\textsuperscript{5},
Bahram Namjou\textsuperscript{6},
Krzysztof Kiryluk\textsuperscript{7},
Iftikhar Kullo\textsuperscript{8},
Yuan Luo\textsuperscript{9},
Blair D. Sullivan\textsuperscript{10},
Benjamin F. Voight\textsuperscript{11,12,13},
Carsten Skarke\textsuperscript{13},
Marylyn D. Ritchie\textsuperscript{1},
Struan F.A. Grant\textsuperscript{3,14,15,1},
eMERGE Consortium\textsuperscript{*} \&
Casey S. Greene~\textsuperscript{\protect\hyperlink{correspondence}{\Letter}} \textsuperscript{16,2}

@@

\textsuperscript{1} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{2} Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{3} Center for Spatial and Functional Genomics, Children's Hospital of Philadelphia, Philadelphia, PA 19104, USA.
\textsuperscript{4} Department of Biomedical Data Science, Stanford University, Stanford, CA 94305, USA.
\textsuperscript{5} Vanderbilt University Medical Center, Nashville, TN 37232, USA.
\textsuperscript{6} Cincinnati Children's Hospital Medical Center, Cincinnati, OH 45229, USA.
\textsuperscript{7} Department of Medicine, Division of Nephrology, Vagelos College of Physicians \& Surgeons, Columbia University, New York, NY 10032, USA.
\textsuperscript{8} Mayo Clinic, Rochester, MN 55905, USA.
\textsuperscript{9} Northwestern University, Chicago, IL 60611, USA.
\textsuperscript{10} Kahlert School of Computing, University of Utah, Salt Lake City, UT 84112, USA.
\textsuperscript{11} Department of Systems Pharmacology and Translational Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{12} Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{13} Institute for Translational Medicine and Therapeutics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA.
\textsuperscript{14} Division of Endocrinology and Diabetes, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA.
\textsuperscript{15} Division of Human Genetics, Children's Hospital of Philadelphia, Philadelphia, PA, 19104, USA; Department of Pediatrics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA, 19104, USA.
\textsuperscript{16} Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA.
\textsuperscript{*}A list of authors and their affiliations appears at the end of the paper.

@@

\hypertarget{emergeconsortium}{%
\subsection{eMERGE Consortium}\label{emergeconsortium}}

Wei-Qi Wei\textsuperscript{5},
Qiping Feng\textsuperscript{5},
Bahram Namjou\textsuperscript{6},
Krzysztof Kiryluk\textsuperscript{7},
Iftikhar Kullo\textsuperscript{8},
Yuan Luo\textsuperscript{9} \&
Marylyn D. Ritchie\textsuperscript{1}
